---
title: "NEST - R2B5 Mesh in Stress Urinary Incontinence: Aggregate Descriptive Statistics for Cohort Which Does Not Exclude Prior Prolapse"
author: "Author"
date: "<small>`r Sys.Date()`</small>"
output: 
  html_document:
    toc: yes
    toc_depth: 2
    number_sections: true
    toc_float:
      collapsed: false
    code_folding: hide
    theme: cerulean
css: rmarkdownstyle.css
---
<button id="toc-toggle" type="button" class="btn btn-default btn-xs code-folding-btn pull-right collapsed" onclick="toggletoc()"><span>Outline</span></button>
<script>
function toggletoc(){
$("#TOC").toggle();
}
</script>
```{r setup, echo=FALSE, results='hide'}
.libPaths("U:/NEST/Analysis/Rlibrary")
p <- "U://NEST//Analysis//Aggregate"
setwd(p)
options(digits=3, width=130, scipen=20, max.print=1500)
require(Hmisc)
require(kableExtra)
require(dplyr)
require(purrr)
require(tidyverse)
require(writexl)
require(DescTools)
source('./Functions.R') 
source('./Ordered_Lists.R')
label_struct <- read_csv("Label_Structured.csv")
label_chart <- read_csv("Label_Chart.csv")
label_compare <- read_csv("Label_Compare.csv")
# Structured-Data Identified EHR Mesh Cohort
factor_mesh <- load_factor("Factor_Descriptives_Overall_Not_Restricted_NLP.csv")
factor_mesh <- merge(factor_mesh, label_struct, by="field", all.x=TRUE)
num_mesh <- load_numeric("Numeric_Descriptives_Overall_Not_Restricted_NLP.csv")
num_mesh <- merge(num_mesh, label_struct, by="field", all.x=TRUE)
# NLP-Identified EHR Mesh Cohort
factor_mesh_rest <- load_factor("Factor_Descriptives_Overall_Restricted_NLP_Mesh.csv")
factor_mesh_rest <- merge(factor_mesh_rest, label_struct, by="field", all.x=TRUE)
num_mesh_rest <- load_numeric("Numeric_Descriptives_Overall_Restricted_NLP_Mesh.csv")
num_mesh_rest <- merge(num_mesh_rest, label_struct, by="field", all.x=TRUE)
## Adj Sling
factor_as_rest <- load_factor("Factor_Descriptives_Adj_Sling_Restricted_NLP_Mesh.csv")
factor_as_rest <- merge(factor_as_rest, label_struct, by="field", all.x=TRUE)
num_as_rest <- load_numeric("Numeric_Descriptives_Adj_Sling_Restricted_NLP_Mesh.csv")
num_as_rest <- merge(num_as_rest, label_struct, by="field", all.x=TRUE)
## Retropubic
factor_ret_rest <- load_factor("Factor_Descriptives_Retropubic_Restricted_NLP_Mesh.csv")
factor_ret_rest <- merge(factor_ret_rest, label_struct, by="field", all.x=TRUE)
num_ret_rest <- load_numeric("Numeric_Descriptives_Retropubic_Restricted_NLP_Mesh.csv")
num_ret_rest <- merge(num_ret_rest, label_struct, by="field", all.x=TRUE)
## Single Incision
factor_si_rest <- load_factor("Factor_Descriptives_Sngl_Inc_Restricted_NLP_Mesh.csv")
factor_si_rest <- merge(factor_si_rest, label_struct, by="field", all.x=TRUE)
num_si_rest <- load_numeric("Numeric_Descriptives_Sngl_Inc_Restricted_NLP_Mesh.csv")
num_si_rest <- merge(num_si_rest, label_struct, by="field", all.x=TRUE)
## Transob
factor_tra_rest <- load_factor("Factor_Descriptives_Transob_Restricted_NLP_Mesh.csv")
factor_tra_rest <- merge(factor_tra_rest, label_struct, by="field", all.x=TRUE)
num_tra_rest <- load_numeric("Numeric_Descriptives_Transob_Restricted_NLP_Mesh.csv")
num_tra_rest <- merge(num_tra_rest, label_struct, by="field", all.x=TRUE)
## Unknown Approach
factor_un_rest <- load_factor("Factor_Descriptives_Unknown_Restricted_NLP_Mesh.csv")
factor_un_rest <- merge(factor_un_rest, label_struct, by="field", all.x=TRUE)
num_un_rest <- load_numeric("Numeric_Descriptives_Unknown_Restricted_NLP_Mesh.csv")
num_un_rest <- merge(num_un_rest, label_struct, by="field", all.x=TRUE)
# Short Chart Review
factor_short_struct <- load_factor("Factor_Descriptives_SCR_All_Not_Restricted_NLP.csv")
factor_short_struct <- merge(factor_short_struct, label_chart, by="field", all.x=TRUE)
factor_short_struct_rest <- load_factor("Factor_Descriptives_SCR_All_Restricted_NLP_Mesh.csv")
factor_short_struct_rest <- merge(factor_short_struct_rest, label_chart, by="field", all.x=TRUE)
# NLP-Identified Sample (Full) Chart Review
factor_full_rest <- load_factor("Factor_Descriptives_FCR_Overall_Restricted_NLP_Mesh.csv")
factor_full_rest <- merge(factor_full_rest, label_chart, by="field", all.x=TRUE)
num_full_rest <- load_numeric("Numeric_Descriptives_FCR_Overall_Restricted_NLP_Mesh.csv")
num_full_rest <- merge(num_full_rest, label_chart, by="field", all.x=TRUE)
## Adj Sling 
factor_full_as_rest <- load_factor("Factor_Descriptives_FCR_Adj_Sling_Restricted_NLP_Mesh.csv")
factor_full_as_rest <- merge(factor_full_as_rest, label_chart, by="field", all.x=TRUE)
num_full_as_rest <- load_numeric("Numeric_Descriptives_FCR_Adj_Sling_Restricted_NLP_Mesh.csv")
num_full_as_rest <- merge(num_full_as_rest, label_chart, by="field", all.x=TRUE)
## Retropubic
factor_full_ret_rest <- load_factor("Factor_Descriptives_FCR_Retropubic_Restricted_NLP_Mesh.csv")
factor_full_ret_rest <- merge(factor_full_ret_rest, label_chart, by="field", all.x=TRUE)
num_full_ret_rest <- load_numeric("Numeric_Descriptives_FCR_Retropubic_Restricted_NLP_Mesh.csv")
num_full_ret_rest <- merge(num_full_ret_rest, label_chart, by="field", all.x=TRUE)
## Single Incision
factor_full_si_rest <- load_factor("Factor_Descriptives_FCR_Sngl_Inc_Restricted_NLP_Mesh.csv")
factor_full_si_rest <- merge(factor_full_si_rest, label_chart, by="field", all.x=TRUE)
num_full_si_rest <- load_numeric("Numeric_Descriptives_FCR_Sngl_Inc_Restricted_NLP_Mesh.csv")
num_full_si_rest <- merge(num_full_si_rest, label_chart, by="field", all.x=TRUE)
## Transob
factor_full_tra_rest <- load_factor("Factor_Descriptives_FCR_Transob_Restricted_NLP_Mesh.csv")
factor_full_tra_rest <- merge(factor_full_tra_rest, label_chart, by="field", all.x=TRUE)
num_full_tra_rest <- load_numeric("Numeric_Descriptives_FCR_Transob_Restricted_NLP_Mesh.csv")
num_full_tra_rest <- merge(num_full_tra_rest, label_chart, by="field", all.x=TRUE)
## Unknown
factor_full_un_rest <- load_factor("Factor_Descriptives_FCR_Unknown_Restricted_NLP_Mesh.csv")
factor_full_un_rest <- merge(factor_full_un_rest, label_chart, by="field", all.x=TRUE)
num_full_un_rest <- load_numeric("Numeric_Descriptives_FCR_Unknown_Restricted_NLP_Mesh.csv")
num_full_un_rest <- merge(num_full_un_rest, label_chart, by="field", all.x=TRUE)
# Compare NLP-identified structured vs. full chart review
factor_comp_sfcr_rest <- load_comp("CompareSFCR_Factor_Overall_Restricted_NLP_Mesh.csv")
factor_comp_sfcr_rest <- merge(factor_comp_sfcr_rest, label_compare, by="field", all.x=TRUE)
num_comp_sfcr_rest <- load_comp("CompareSFCR_Numeric_Overall_Restricted_NLP_Mesh.csv")
num_comp_sfcr_rest <- merge(num_comp_sfcr_rest, label_compare, by="field", all.x=TRUE)
## Adj Sling
factor_comp_sfcr_as_rest <- load_comp("CompareSFCR_Factor_Adj_Sling_Restricted_NLP_Mesh.csv")
factor_comp_sfcr_as_rest <- merge(factor_comp_sfcr_as_rest, label_compare, by="field", all.x=TRUE)
num_comp_sfcr_as_rest <- load_comp("CompareSFCR_Numeric_Adj_Sling_Restricted_NLP_Mesh.csv")
num_comp_sfcr_as_rest <- merge(num_comp_sfcr_as_rest, label_compare, by="field", all.x=TRUE)
## Retropubic
factor_comp_sfcr_ret_rest <- load_comp("CompareSFCR_Factor_Retropubic_Restricted_NLP_Mesh.csv")
factor_comp_sfcr_ret_rest <- merge(factor_comp_sfcr_ret_rest, label_compare, by="field", all.x=TRUE)
num_comp_sfcr_ret_rest <- load_comp("CompareSFCR_Numeric_Retropubic_Restricted_NLP_Mesh.csv")
num_comp_sfcr_ret_rest <- merge(num_comp_sfcr_ret_rest, label_compare, by="field", all.x=TRUE)
## Single Incision
factor_comp_sfcr_si_rest <- load_comp("CompareSFCR_Factor_Sngl_Inc_Restricted_NLP_Mesh.csv")
factor_comp_sfcr_si_rest <- merge(factor_comp_sfcr_si_rest, label_compare, by="field", all.x=TRUE)
num_comp_sfcr_si_rest <- load_comp("CompareSFCR_Numeric_Sngl_Inc_Restricted_NLP_Mesh.csv")
num_comp_sfcr_si_rest <- merge(num_comp_sfcr_si_rest, label_compare, by="field", all.x=TRUE)
## Transob
factor_comp_sfcr_tra_rest <- load_comp("CompareSFCR_Factor_Transob_Restricted_NLP_Mesh.csv")
factor_comp_sfcr_tra_rest <- merge(factor_comp_sfcr_tra_rest, label_compare, by="field", all.x=TRUE)
num_comp_sfcr_tra_rest <- load_comp("CompareSFCR_Numeric_Transob_Restricted_NLP_Mesh.csv")
num_comp_sfcr_tra_rest <- merge(num_comp_sfcr_tra_rest, label_compare, by="field", all.x=TRUE)
## Unknown
factor_comp_sfcr_un_rest <- load_comp("CompareSFCR_Factor_Unknown_Restricted_NLP_Mesh.csv")
factor_comp_sfcr_un_rest <- merge(factor_comp_sfcr_un_rest, label_compare, by="field", all.x=TRUE)
num_comp_sfcr_un_rest <- load_comp("CompareSFCR_Numeric_Unknown_Restricted_NLP_Mesh.csv")
num_comp_sfcr_un_rest <- merge(num_comp_sfcr_un_rest, label_compare, by="field", all.x=TRUE)
# Compare NLP Approach & Mesh vs. chart review (gold standard)
factor_comp_rscr <- load_comp("CompareRSCR_Factor_Overall_Not_Restricted_NLP.csv")
factor_comp_rscr <- merge(factor_comp_rscr, label_compare, by="field", all.x=TRUE)
# Compare EHR Mesh vs. chart review (gold standard)
factor_comp_sscr <- load_comp("CompareSSCR_Factor_Overall_Not_Restricted_NLP.csv")
factor_comp_sscr <- merge(factor_comp_sscr, label_compare, by="field", all.x=TRUE)
# Compare EHR Mesh vs. NLP (gold standard)
factor_comp_rs <- load_comp("CompareRS_Factor_Overall_Not_Restricted_NLP.csv")
factor_comp_rs <- merge(factor_comp_rs, label_compare, by="field", all.x=TRUE)
Hmisc::knitrSet(lang='markdown', fig.path='png/', fig.align='left', w=6.5, h=2)
mu <- markupSpecs$html
cap <- mu$cap
lcap <- mu$lcap
```
# Methods
This final report includes data from Cornell, Lahey, Mayo, VUMC, and Yale. Patients were included if they were women aged 18 years or greater, underwent a procedure for stress urinary incontinence (SUI) with or without mesh implantation after 1/1/2010, and had at least one primary care, OB/GYN, or Urology visit in the year prior to the procedure. Patients were excluded for prior SUI surgery or prior diagnosis of a urethral diverticulum or any urinary-genital tract fistula in the 90 days prior to the index surgery. For patients with multiple procedures for SUI, the first procedure was selected. Small counts between 1 and 10 are censored as "[1-10]" per guidelines to prevent re-identification of patients. 

The site-specific descriptive statistics were calculated by each of the five sites. VUMC merged the results and generated the aggregate descriptive statistics. Weighted means and weighted standard deviations were calculated using the wtd.mean and wtd.var functions from the R package Hmisc, where the weights are the proportion of patients contributed from each site out of the total N.

# Sites Included in Aggregate Report
```{r, results='asis'}
nsites <- 5 #updated 7/17/22
nsites_c <- 5
s <- c("Cornell", "Lahey", "Mayo", "VUMC", "Yale")
y <- c("Yes", "Yes", "Yes", "Yes", "Yes")
sy <- cbind(s,y)
colnames(sy) <- c("Site", "Included")
knitr::kable(sy, align='lc', "html", col.names=colnames(sy), escape=FALSE,
             table.attr='class="table-fixed-header"') %>%
    kable_styling(position="left", full_width=FALSE, bootstrap_options=c("striped", "condensed"))
```

# Flowchart for inclusion and exclusion criteria overall and each site within the NLP-integrated cohort
Columns summarize N or n excluded (cumulative n excluded). 
```{r}
flow_chart <- list.files(path=p, pattern = "Flowchart.csv", full.names=TRUE) %>%
  map_df(~read_csv(.x, col_types = cols(.default="c"))) 
flow_chart <- data.frame(flow_chart)
# Some sites had greater number no/indeterminate Mesh than number with prior prolapse
flow_chart[35,2] <- 0 #Mayo
flow_chart[59,2] <- 0 #Yale
flow_chart_site <- flow_chart %>%
  group_by(X1) %>%
  gather("n_dropped", key=variable, value=number) %>%
  unite(combi, variable, site) %>%
  spread(combi, number)
flow_chart_agg <- flow_chart %>%
  group_by(X1) %>%
  mutate(n_dropped = ifelse(n_dropped == "[1-10]", 1, as.numeric(n_dropped)),
         aggregate_n_dropped = cumsum(n_dropped))
tf <- data.frame(tail(flow_chart_agg, n=length(flow_chart_agg$X1)/nsites_c))
flow_final <- merge(tf, flow_chart_site, all.x=TRUE, by="X1")
flow_final <- flow_final[match(order_flow, flow_final$X1),]
flow_final <- flow_final[-c(11, 12),-c(2,3)] #Drop rows which exclude prior prolapse & restrict NLP mesh
flow_cumul <- flow_final %>%
  mutate(n_dropped_Cornell_r = ifelse(n_dropped_Cornell == "[1-10]", 1, as.numeric(n_dropped_Cornell)),
         n_dropped_Mayo_r = ifelse(n_dropped_Mayo == "[1-10]", 1, as.numeric(n_dropped_Mayo)),
         n_dropped_Lahey_r = ifelse(n_dropped_Lahey == "[1-10]", 1, as.numeric(n_dropped_Lahey)),
         n_dropped_VUMC_r = ifelse(n_dropped_VUMC == "[1-10]", 1, as.numeric(n_dropped_VUMC)),
         n_dropped_Yale_r = ifelse(n_dropped_Yale == "[1-10]", 1, as.numeric(n_dropped_Yale)))
flow_cumul <- flow_cumul %>%
  mutate(aggregate_n_dropped_cs = cumsum(aggregate_n_dropped),
         n_dropped_Cornell_cs = cumsum(n_dropped_Cornell_r),
         n_dropped_Mayo_cs = cumsum(n_dropped_Mayo_r),
         n_dropped_Lahey_cs = cumsum(n_dropped_Lahey_r),
         n_dropped_VUMC_cs = cumsum(n_dropped_VUMC_r),
         n_dropped_Yale_cs = cumsum(n_dropped_Yale_r))
flow_cumul <- flow_cumul %>%
  mutate(print_Overall = paste(aggregate_n_dropped, " (", aggregate_n_dropped_cs, ")", sep=""),
         print_Cornell = paste(n_dropped_Cornell, " (", n_dropped_Cornell_cs, ")", sep=""),
         print_Lahey = paste(n_dropped_Lahey, " (", n_dropped_Lahey_cs, ")", sep=""),
         print_Mayo = paste(n_dropped_Mayo, " (", n_dropped_Mayo_cs, ")", sep=""),
         print_VUMC = paste(n_dropped_VUMC, " (", n_dropped_VUMC_cs, ")", sep=""),
         print_Yale = paste(n_dropped_Yale, " (", n_dropped_Yale_cs, ")", sep=""))
exc_rest <- flow_cumul[10,c("aggregate_n_dropped_cs", "n_dropped_Cornell_cs", "n_dropped_Lahey_cs",   
                            "n_dropped_Mayo_cs", "n_dropped_VUMC_cs", "n_dropped_Yale_cs")]
flow_cumul <- flow_cumul[,c(1,19:24)]
tot_rest <- matrix(c(4016, 1059, 535, 1177, 938, 307), nrow=1, ncol=6, byrow=TRUE)
first_row <- exc_rest + tot_rest
tot_rest <- cbind("Count of all procedures included (N)", tot_rest)
first_row <- cbind("Include women aged 18y+, had surgery for stress urinary incontinence with or without mesh implantation after 1/1/2010, and had 1+ primary care, OB/GYN, or Urology visit(s) in the year prior to the procedure (N)", first_row)
colnames(tot_rest) <- colnames(flow_cumul)
colnames(first_row) <- colnames(flow_cumul)
flow_final <- rbind(first_row, flow_cumul, tot_rest)
colnames(flow_final) <- gsub('print_', '', colnames(flow_final))
colnames(flow_final) <- gsub('X1', 'Inclusion/Exclusion Criteria', colnames(flow_final))
knitr::kable(flow_final, align='lcccccc', "html", col.names=colnames(flow_final), escape=FALSE,
             table.attr='class="table-fixed-header"') %>%
    kable_styling(position="left", full_width=TRUE, bootstrap_options=c("striped", "condensed"))
```

# Results of Structured-Data Identified EHR Mesh Cohort
## Overall
### Demographics
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_mesh, dat_numeric=num_mesh,
           gp="Demographics", fo=order_dem_fac, no=order_dem_num,
           ns=nsites_c)
```

### Prior Medical History
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_mesh, dat_numeric=num_mesh,
           gp="Prior Medical History", fo=order_med_fac, no=order_med_num,
           ns=nsites_c)
```

### Active Medications
Drug Class ATC
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_mesh, dat_numeric=num_mesh,
           gp="Active Medications", fo=order_drug_fac, no=order_drug_num,
           ns=nsites_c)
```

### Labs
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_mesh, dat_numeric=num_mesh, 
           gp="Labs", fo=order_lab_fac, no=order_lab_num,
           ns=nsites_c)
```

### Primary Procedure Characteristics
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_mesh, dat_numeric=num_mesh,
           gp="Primary Procedure Characteristics", fo=order_nlp_fac, no=order_nlp_num,
           ns=nsites_c)
```

### Outcomes
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_mesh, dat_numeric=num_mesh,
           gp="Outcomes", fo=order_out_fac, no=order_out_num,
           ns=nsites_c)
```

# Results of NLP-Identified EHR Mesh Cohort
## Overall
### Demographics
Columns summarize n (%) or mean (SD) and [missing count], where applicable. 
```{r, results='asis'}
print_miss(dat_factor=factor_mesh_rest, dat_numeric=num_mesh_rest,
           gp="Demographics", fo=order_dem_fac, no=order_dem_num,
           ns=nsites_c)
```

### Prior Medical History
Columns summarize n (%) or mean (SD) and [missing count], where applicable. 
```{r, results='asis'}
print_miss(dat_factor=factor_mesh_rest, dat_numeric=num_mesh_rest,
           gp="Prior Medical History", fo=order_med_fac, no=order_med_num,
           ns=nsites_c)
```

### Active Medications
Drug Class ATC
Columns summarize n (%) or mean (SD) and [missing count], where applicable. 
```{r, results='asis'}
print_miss(dat_factor=factor_mesh_rest, dat_numeric=num_mesh_rest,
           gp="Active Medications", fo=order_drug_fac, no=order_drug_num,
           ns=nsites_c)
```

### Labs
Columns summarize n (%) or mean (SD) and [missing count], where applicable. 
```{r, results='asis'}
print_miss(dat_factor=factor_mesh_rest, dat_numeric=num_mesh_rest, 
           gp="Labs", fo=order_lab_fac, no=order_lab_num,
           ns=nsites_c)
```

### Primary Procedure Characteristics
Columns summarize n (%) or mean (SD) and [missing count], where applicable. 
```{r, results='asis'}
print_miss(dat_factor=factor_mesh_rest, dat_numeric=num_mesh_rest,
           gp="Primary Procedure Characteristics", fo=order_nlp_fac, no=order_nlp_num,
           ns=nsites_c)
```

### Outcomes
Columns summarize n (%) or mean (SD) and [missing count], where applicable. 
```{r, results='asis'}
print_miss(dat_factor=factor_mesh_rest, dat_numeric=num_mesh_rest,
           gp="Outcomes", fo=order_out_fac, no=order_out_num,
           ns=nsites_c)
```

## NLP Approach: Adjustable Sling (AMUS)
### Demographics
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_as_rest, dat_numeric=num_as_rest,
           gp="Demographics", fo=order_dem_fac, no=order_dem_num)
```

### Prior Medical History
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_as_rest, dat_numeric=num_as_rest,
           gp="Prior Medical History", fo=order_med_fac, no=order_med_num)
```

### Active Medications
Drug Class ATC
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_as_rest, dat_numeric=num_as_rest,
           gp="Active Medications", fo=order_drug_fac, no=order_drug_num)
```

### Labs
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_as_rest, dat_numeric=num_as_rest, 
           gp="Labs", fo=order_lab_fac, no=order_lab_num)
```

### Primary Procedure Characteristics
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_as_rest, dat_numeric=num_as_rest,
           gp="Primary Procedure Characteristics", fo=order_nlp_fac, no=order_nlp_num)
```

### Outcomes
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_as_rest, dat_numeric=num_as_rest,
           gp="Outcomes", fo=order_out_fac, no=order_out_num)
```

## NLP Approach: Retro-Pubic (RPMUS)
### Demographics
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_ret_rest, dat_numeric=num_ret_rest,
           gp="Demographics", fo=order_dem_fac, no=order_dem_num)
```

### Prior Medical History
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_ret_rest, dat_numeric=num_ret_rest,
           gp="Prior Medical History", fo=order_med_fac, no=order_med_num)
```

### Active Medications
Drug Class ATC
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_ret_rest, dat_numeric=num_ret_rest,
           gp="Active Medications", fo=order_drug_fac, no=order_drug_num)
```

### Labs
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_ret_rest, dat_numeric=num_ret_rest, 
           gp="Labs", fo=order_lab_fac, no=order_lab_num)
```

### Primary Procedure Characteristics
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_ret_rest, dat_numeric=num_ret_rest,
           gp="Primary Procedure Characteristics", fo=order_nlp_fac, no=order_nlp_num)
```

### Outcomes
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_ret_rest, dat_numeric=num_ret_rest,
           gp="Outcomes", fo=order_out_fac, no=order_out_num)
```

## NLP Approach: Single Incision (SIMUS)
### Demographics
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_si_rest, dat_numeric=num_si_rest,
           gp="Demographics", fo=order_dem_fac, no=order_dem_num)
```

### Prior Medical History
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_si_rest, dat_numeric=num_si_rest,
           gp="Prior Medical History", fo=order_med_fac, no=order_med_num)
```

### Active Medications
Drug Class ATC
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_si_rest, dat_numeric=num_si_rest,
           gp="Active Medications", fo=order_drug_fac, no=order_drug_num)
```

### Labs
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_si_rest, dat_numeric=num_si_rest, 
           gp="Labs", fo=order_lab_fac, no=order_lab_num)
```

### Primary Procedure Characteristics
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_si_rest, dat_numeric=num_si_rest,
           gp="Primary Procedure Characteristics", fo=order_nlp_fac, no=order_nlp_num)
```

### Outcomes
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_si_rest, dat_numeric=num_si_rest,
           gp="Outcomes", fo=order_out_fac, no=order_out_num)
```

## NLP Approach: Trans-Obturator (TOMUS)
### Demographics
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_tra_rest, dat_numeric=num_tra_rest,
           gp="Demographics", fo=order_dem_fac, no=order_dem_num)
```

### Prior Medical History
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_tra_rest, dat_numeric=num_tra_rest,
           gp="Prior Medical History", fo=order_med_fac, no=order_med_num)
```

### Active Medications
Drug Class ATC
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_tra_rest, dat_numeric=num_tra_rest,
           gp="Active Medications", fo=order_drug_fac, no=order_drug_num)
```

### Labs
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_tra_rest, dat_numeric=num_tra_rest, 
           gp="Labs", fo=order_lab_fac, no=order_lab_num)
```

### Primary Procedure Characteristics
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_tra_rest, dat_numeric=num_tra_rest,
           gp="Primary Procedure Characteristics", fo=order_nlp_fac, no=order_nlp_num)
```

### Outcomes
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_tra_rest, dat_numeric=num_tra_rest,
           gp="Outcomes", fo=order_out_fac, no=order_out_num)
```

## NLP Approach: Unknown
### Demographics
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_un_rest, dat_numeric=num_un_rest,
           gp="Demographics", fo=order_dem_fac, no=order_dem_num)
```

### Prior Medical History
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_un_rest, dat_numeric=num_un_rest,
           gp="Prior Medical History", fo=order_med_fac, no=order_med_num)
```

### Active Medications
Drug Class ATC
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_un_rest, dat_numeric=num_un_rest,
           gp="Active Medications", fo=order_drug_fac, no=order_drug_num)
```

### Labs
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_un_rest, dat_numeric=num_un_rest, 
           gp="Labs", fo=order_lab_fac, no=order_lab_num)
```

### Primary Procedure Characteristics
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_un_rest, dat_numeric=num_un_rest,
           gp="Primary Procedure Characteristics", fo=order_nlp_fac, no=order_nlp_num)
```

### Outcomes
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_un_rest, dat_numeric=num_un_rest,
           gp="Outcomes", fo=order_out_fac, no=order_out_num)
```

# Aggregate Results of NLP-Identified EHR Mesh Cohort
## Demographics
Columns summarize n (%) or mean (SD) and [missing count], where applicable. Subgroup n's may not sum to overall n due to censoring.
```{r, results='asis'}
print_miss(fmr=factor_mesh_rest, far=factor_as_rest,
           frr=factor_ret_rest, fir=factor_si_rest,
           ftr=factor_tra_rest, fur=factor_un_rest,
           nmr=num_mesh_rest, nar=num_as_rest,
           nrr=num_ret_rest, nir=num_si_rest,
           ntr=num_tra_rest, nur=num_un_rest,
           gp="Demographics", fo=order_dem_fac, no=order_dem_num, 
           agg=TRUE, ns=nsites, nsc=nsites_c)
```

## Prior Medical History
Columns summarize n (%) or mean (SD) and [missing count], where applicable. Subgroup n's may not sum to overall n due to censoring. 
```{r, results='asis'}
print_miss(fmr=factor_mesh_rest, far=factor_as_rest,
           frr=factor_ret_rest, fir=factor_si_rest,
           ftr=factor_tra_rest, fur=factor_un_rest,
           nmr=num_mesh_rest, nar=num_as_rest,
           nrr=num_ret_rest, nir=num_si_rest,
           ntr=num_tra_rest, nur=num_un_rest,
           gp="Prior Medical History", fo=order_med_fac, no=order_med_num, 
           agg=TRUE, ns=nsites, nsc=nsites_c)
```

## Active Medications
Drug Class ATC
Columns summarize n (%) or mean (SD) and [missing count], where applicable. Subgroup n's may not sum to overall n due to censoring. 
```{r, results='asis'}
print_miss(fmr=factor_mesh_rest, far=factor_as_rest,
           frr=factor_ret_rest, fir=factor_si_rest,
           ftr=factor_tra_rest, fur=factor_un_rest,
           nmr=num_mesh_rest, nar=num_as_rest,
           nrr=num_ret_rest, nir=num_si_rest,
           ntr=num_tra_rest, nur=num_un_rest,
           gp="Active Medications", fo=order_drug_fac, no=order_drug_num, 
           agg=TRUE, ns=nsites, nsc=nsites_c)
```

## Labs
Columns summarize n (%) or mean (SD) and [missing count], where applicable. Subgroup n's may not sum to overall n due to censoring. 
```{r, results='asis'}
print_miss(fmr=factor_mesh_rest, far=factor_as_rest,
           frr=factor_ret_rest, fir=factor_si_rest,
           ftr=factor_tra_rest, fur=factor_un_rest,
           nmr=num_mesh_rest, nar=num_as_rest,
           nrr=num_ret_rest, nir=num_si_rest,
           ntr=num_tra_rest, nur=num_un_rest,
           gp="Labs", fo=order_lab_fac, no=order_lab_num, 
           agg=TRUE, ns=nsites, nsc=nsites_c)
```

## Primary Procedure Characteristics
Columns summarize n (%) or mean (SD) and [missing count], where applicable. Subgroup n's may not sum to overall n due to censoring. 
```{r, results='asis'}
print_miss(fmr=factor_mesh_rest, far=factor_as_rest,
           frr=factor_ret_rest, fir=factor_si_rest,
           ftr=factor_tra_rest, fur=factor_un_rest,
           nmr=num_mesh_rest, nar=num_as_rest,
           nrr=num_ret_rest, nir=num_si_rest,
           ntr=num_tra_rest, nur=num_un_rest,
           gp="Primary Procedure Characteristics", fo=order_nlp_fac, 
           no=order_nlp_num, agg=TRUE, ns=nsites, nsc=nsites_c)
```

## Outcomes
Columns summarize n (%) or mean (SD) and [missing count], where applicable. Subgroup n's may not sum to overall n due to censoring. 
```{r, results='asis'}
print_miss(fmr=factor_mesh_rest, far=factor_as_rest,
           frr=factor_ret_rest, fir=factor_si_rest,
           ftr=factor_tra_rest, fur=factor_un_rest,
           nmr=num_mesh_rest, nar=num_as_rest,
           nrr=num_ret_rest, nir=num_si_rest,
           ntr=num_tra_rest, nur=num_un_rest,
           gp="Outcomes", fo=order_out_fac, no=order_out_num, 
           agg=TRUE, ns=nsites, nsc=nsites_c)
```

# Results of Structured Data-Identified Short Chart Review
## Primary Procedure Characteristics
Columns summarize n (%) and [missing count].
```{r, results='asis'}
ra <- prep_miss_site(factor_short_struct, grouping="Primary Procedure Characteristics",
                     order_gp=order_chart_short, n_sites=nsites_c, fac=TRUE)
knitr::kable(ra, align='lccccc', "html", col.names=colnames(ra), escape=FALSE,
             table.attr='class="table-fixed-header"') %>%
    kable_styling(position="left", full_width=TRUE, bootstrap_options=c("striped", "hover", "condensed")) %>%
    scroll_box(height="500px")
```

# Results of NLP-Identified Short Chart Review
## Primary Procedure Characteristics
Columns summarize n (%) and [missing count]. 
```{r, results='asis'}
ra <- prep_miss_site(factor_short_struct_rest, grouping="Primary Procedure Characteristics",
                     order_gp=order_chart_short, n_sites=nsites_c, fac=TRUE)
knitr::kable(ra, align='lccccc', "html", col.names=colnames(ra), escape=FALSE,
             table.attr='class="table-fixed-header"') %>%
    kable_styling(position="left", full_width=TRUE, bootstrap_options=c("striped", "hover", "condensed")) %>%
    scroll_box(height="500px")
```

# Aggregate Results of NLP-Identified Short Chart Review
## Primary Procedure Characteristics
Columns summarize n (%) and [missing count]. 
```{r, results='asis'}
alldat=factor_short_struct_rest
grouping="Primary Procedure Characteristics"
order_gp=order_chart_short
nsic=nsites_c
# Overall
rasc <- alldat[alldat$group == grouping,]
rasc <- rasc[with(rasc, order(site)),]
rasc <- rasc %>%
  group_by(label) %>%
  mutate(n_nonmiss = ifelse(n_nonmiss == "[1-10]", 1, as.numeric(n_nonmiss)),
         aggregate_n_missing = cumsum(n_missing),
         n_yes = ifelse(n_yes == "[1-10]", 1, as.numeric(n_yes)),
         aggregate_n_yes = cumsum(n_yes),
         aggregate_n_nonmiss = cumsum(n_nonmiss),
         aggregate_perc_yes = format(round(100*(aggregate_n_yes / aggregate_n_nonmiss), digits=0), nsms=0),
         print_Overall = paste(aggregate_n_yes, " (", aggregate_perc_yes, "%); [", 
                               aggregate_n_missing, "]", sep=""))
rasc_cut <- data.frame(tail(rasc, n=length(rasc$label)/nsic))
rasc_cut <- rasc_cut[match(order_gp, rasc_cut$field),]
rasc_sub <- rasc_cut[, c("label", "print_Overall")]
colnames(rasc_sub) <- c("Field", "Overall")
knitr::kable(rasc_sub, align='lccccc', "html", col.names=colnames(rasc_sub), escape=FALSE,
               table.attr='class="table-fixed-header"') %>%
    kable_styling(position="left", full_width=TRUE, bootstrap_options=c("striped", "hover", "condensed")) %>%
    scroll_box(height="500px")
```

# Results of NLP-Identified Sample Chart Review
## Overall
### Prior Medical History
Columns summarize n (%) or mean (SD) and [missing count], where applicable. 
```{r, results='asis'}
print_miss(dat_factor=factor_full_rest, dat_numeric=num_full_rest, gp="Prior Medical History",
           fo=order_chart_med_fac, no=order_chart_med_num, ns=nsites_c)
```

### Primary Procedure Characteristics
Columns summarize n (%) or mean (SD) and [missing count], where applicable. 
```{r, results='asis'}
print_miss(dat_factor=factor_full_rest, dat_numeric=num_full_rest, gp="Primary Procedure Characteristics",
           fo=order_chart_pro_fac, no=order_chart_pro_num, ns=nsites_c)
```

### Outcomes 
Columns summarize n (%) or mean (SD) and [missing count], where applicable. 
```{r, results='asis'}
print_miss(dat_factor=factor_full_rest, dat_numeric=num_full_rest, gp="Outcomes", 
           fo=order_chart_out_fac, no=order_chart_out_num, ns=nsites_c)
```

## NLP Approach: Adjustable Sling (AMUS)
### Prior Medical History
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_full_as_rest, dat_numeric=num_full_as_rest, gp="Prior Medical History",
           fo=order_chart_med_fac, no=order_chart_med_num)
```

### Primary Procedure Characteristics
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_full_as_rest, dat_numeric=num_full_as_rest, gp="Primary Procedure Characteristics",
           fo=order_chart_pro_fac, no=order_chart_pro_num)
```

### Outcomes 
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_full_as_rest, dat_numeric=num_full_as_rest, gp="Outcomes", 
           fo=order_chart_out_fac, no=order_chart_out_num)
```

## NLP Approach: Retro-Pubic (RPMUS)
### Prior Medical History
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_full_ret_rest, dat_numeric=num_full_ret_rest, gp="Prior Medical History",
           fo=order_chart_med_fac, no=order_chart_med_num)
```

### Primary Procedure Characteristics
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_full_ret_rest, dat_numeric=num_full_ret_rest, gp="Primary Procedure Characteristics",
           fo=order_chart_pro_fac, no=order_chart_pro_num)
```

### Outcomes 
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_full_ret_rest, dat_numeric=num_full_ret_rest, gp="Outcomes", 
           fo=order_chart_out_fac, no=order_chart_out_num)
```

## NLP Approach: Single Incision (SIMUS)
### Prior Medical History
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_full_si_rest, dat_numeric=num_full_si_rest, gp="Prior Medical History",
           fo=order_chart_med_fac, no=order_chart_med_num)
```

### Primary Procedure Characteristics
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_full_si_rest, dat_numeric=num_full_si_rest, gp="Primary Procedure Characteristics",
           fo=order_chart_pro_fac, no=order_chart_pro_num)
```

### Outcomes 
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_full_si_rest, dat_numeric=num_full_si_rest, gp="Outcomes", 
           fo=order_chart_out_fac, no=order_chart_out_num)
```

## NLP Approach: Trans-Obturator (TOMUS)
### Prior Medical History
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_full_tra_rest, dat_numeric=num_full_tra_rest, gp="Prior Medical History",
           fo=order_chart_med_fac, no=order_chart_med_num)
```

### Primary Procedure Characteristics
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_full_tra_rest, dat_numeric=num_full_tra_rest, gp="Primary Procedure Characteristics",
           fo=order_chart_pro_fac, no=order_chart_pro_num)
```

### Outcomes 
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_full_tra_rest, dat_numeric=num_full_tra_rest, gp="Outcomes", 
           fo=order_chart_out_fac, no=order_chart_out_num)
```

## NLP Approach: Unknown
### Prior Medical History
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_full_un_rest, dat_numeric=num_full_un_rest, gp="Prior Medical History",
           fo=order_chart_med_fac, no=order_chart_med_num)
```

### Primary Procedure Characteristics
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_full_un_rest, dat_numeric=num_full_un_rest, gp="Primary Procedure Characteristics",
           fo=order_chart_pro_fac, no=order_chart_pro_num)
```

### Outcomes 
Columns summarize n (%) or mean (SD) and [missing count], where applicable.
```{r, results='asis'}
print_miss(dat_factor=factor_full_un_rest, dat_numeric=num_full_un_rest, gp="Outcomes", 
           fo=order_chart_out_fac, no=order_chart_out_num)
```

# Aggregate Results of NLP-Identified Sample Chart Review
## Prior Medical History
Columns summarize n (%) or mean (SD) and [missing count], where applicable. Subgroup n's may not sum to overall n due to censoring. 
```{r, results='asis'}
print_miss(fmr=factor_full_rest, far=factor_full_as_rest,
           frr=factor_full_ret_rest, fir=factor_full_si_rest,
           ftr=factor_full_tra_rest, fur=factor_full_un_rest,
           nmr=num_full_rest, nar=num_full_as_rest,
           nrr=num_full_ret_rest, nir=num_full_si_rest,
           ntr=num_full_tra_rest, nur=num_full_un_rest,
           gp="Prior Medical History", fo=order_chart_med_fac, 
           no=order_chart_med_num, agg=TRUE, ns=nsites, nsc=nsites_c)
```

## Primary Procedure Characteristics
Columns summarize n (%) or mean (SD) and [missing count], where applicable. Subgroup n's may not sum to overall n due to censoring. 
```{r, results='asis'}
print_miss(fmr=factor_full_rest, far=factor_full_as_rest,
           frr=factor_full_ret_rest, fir=factor_full_si_rest,
           ftr=factor_full_tra_rest, fur=factor_full_un_rest,
           nmr=num_full_rest, nar=num_full_as_rest,
           nrr=num_full_ret_rest, nir=num_full_si_rest,
           ntr=num_full_tra_rest, nur=num_full_un_rest,
           gp="Primary Procedure Characteristics", fo=order_chart_pro_fac, 
           no=order_chart_pro_num, agg=TRUE, ns=nsites, nsc=nsites_c)
```

## Outcomes
Columns summarize n (%) or mean (SD) and [missing count], where applicable. Subgroup n's may not sum to overall n due to censoring. 
```{r, results='asis'}
print_miss(fmr=factor_full_rest, far=factor_full_as_rest,
           frr=factor_full_ret_rest, fir=factor_full_si_rest,
           ftr=factor_full_tra_rest, fur=factor_full_un_rest,
           nmr=num_full_rest, nar=num_full_as_rest,
           nrr=num_full_ret_rest, nir=num_full_si_rest,
           ntr=num_full_tra_rest, nur=num_full_un_rest,
           gp="Outcomes", fo=order_chart_out_fac, 
           no=order_chart_out_num, agg=TRUE, ns=nsites, nsc=nsites_c)
```

# Chart Review Validation of NLP-Identified EHR Mesh Cohort
## Data Availability by Site
### Overall
#### Present in Both Structured and Chart Review Data
##### Prior Medical History
Columns summarize n (%). 
```{r, results='asis'}
print_comp(factor_comp_sfcr_rest, num_comp_sfcr_rest, gp="Prior Medical History",
           fo=order_comp_med_fac, no=order_comp_med_num, c="both present",
           agg=FALSE, ns=nsites_c)
```

##### Primary Procedure Characteristics
Columns summarize n (%). 
```{r, results='asis'}
print_comp(factor_comp_sfcr_rest, num_comp_sfcr_rest, gp="Primary Procedure Characteristics",
           fo=order_comp_pro_fac, no=order_comp_pro_num, c="both present",
           agg=FALSE, ns=nsites_c)
```

##### Outcomes
Columns summarize n (%). 
```{r, results='asis'}
print_comp(factor_comp_sfcr_rest, num_comp_sfcr_rest, gp="Outcomes",
           fo=order_comp_out_fac, no=order_comp_out_num, c="both present",
           agg=FALSE, ns=nsites_c)
```

#### Present in Structured Data Only
##### Prior Medical History
Columns summarize n (%). 
```{r, results='asis'}
print_comp(factor_comp_sfcr_rest, num_comp_sfcr_rest, gp="Prior Medical History",
           fo=order_comp_med_fac, no=order_comp_med_num, c="structured only",
           agg=FALSE, ns=nsites_c)
```

##### Primary Procedure Characteristics
Columns summarize n (%). 
```{r, results='asis'}
print_comp(factor_comp_sfcr_rest, num_comp_sfcr_rest, gp="Primary Procedure Characteristics",
           fo=order_comp_pro_fac, no=order_comp_pro_num, c="structured only",
           agg=FALSE, ns=nsites_c)
```

##### Outcomes
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_rest, num_comp_sfcr_rest, gp="Outcomes",
           fo=order_comp_out_fac, no=order_comp_out_num, c="structured only",
           agg=FALSE, ns=nsites_c)
```

#### Present in Chart Review Data Only
##### Prior Medical History
Columns summarize n (%). 
```{r, results='asis'}
print_comp(factor_comp_sfcr_rest, num_comp_sfcr_rest, gp="Prior Medical History",
           fo=order_comp_med_fac, no=order_comp_med_num, c="chart only",
           agg=FALSE, ns=nsites_c)
```

##### Primary Procedure Characteristics
Columns summarize n (%). 
```{r, results='asis'}
print_comp(factor_comp_sfcr_rest, num_comp_sfcr_rest, gp="Primary Procedure Characteristics",
           fo=order_comp_pro_fac, no=order_comp_pro_num, c="chart only",
           agg=FALSE, ns=nsites_c)
```

##### Outcomes
Columns summarize n (%). 
```{r, results='asis'}
print_comp(factor_comp_sfcr_rest, num_comp_sfcr_rest, gp="Outcomes",
           fo=order_comp_out_fac, no=order_comp_out_num, c="chart only",
           agg=FALSE, ns=nsites_c)
```

#### Null in Both Structured and Chart Review Data
##### Prior Medical History
Columns summarize n (%). 
```{r, results='asis'}
print_comp(factor_comp_sfcr_rest, num_comp_sfcr_rest, gp="Prior Medical History",
           fo=order_comp_med_fac, no=order_comp_med_num, c="both null",
           agg=FALSE, ns=nsites_c)
```

##### Primary Procedure Characteristics
Columns summarize n (%). 
```{r, results='asis'}
print_comp(factor_comp_sfcr_rest, num_comp_sfcr_rest, gp="Primary Procedure Characteristics",
           fo=order_comp_pro_fac, no=order_comp_pro_num, c="both null",
           agg=FALSE, ns=nsites_c)
```

##### Outcomes
Columns summarize n (%). 
```{r, results='asis'}
print_comp(factor_comp_sfcr_rest, num_comp_sfcr_rest, gp="Outcomes",
           fo=order_comp_out_fac, no=order_comp_out_num, c="both null",
           agg=FALSE, ns=nsites_c)
```

### NLP Approach: Adjustable Sling (AMUS)
#### Present in Both Structured and Chart Review Data
##### Prior Medical History
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_as_rest, num_comp_sfcr_as_rest, gp="Prior Medical History",
           fo=order_comp_med_fac, no=order_comp_med_num, c="both present",
           agg=FALSE, ns=nsites)
```

##### Primary Procedure Characteristics
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_as_rest, num_comp_sfcr_as_rest, gp="Primary Procedure Characteristics",
           fo=order_comp_pro_fac, no=order_comp_pro_num, c="both present",
           agg=FALSE, ns=nsites)
```

##### Outcomes
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_as_rest, num_comp_sfcr_as_rest, gp="Outcomes",
           fo=order_comp_out_fac, no=order_comp_out_num, c="both present",
           agg=FALSE, ns=nsites)
```

#### Present in Structured Data Only
##### Prior Medical History
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_as_rest, num_comp_sfcr_as_rest, gp="Prior Medical History",
           fo=order_comp_med_fac, no=order_comp_med_num, c="structured only",
           agg=FALSE, ns=nsites)
```

##### Primary Procedure Characteristics
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_as_rest, num_comp_sfcr_as_rest, gp="Primary Procedure Characteristics",
           fo=order_comp_pro_fac, no=order_comp_pro_num, c="structured only",
           agg=FALSE, ns=nsites)
```

##### Outcomes
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_as_rest, num_comp_sfcr_as_rest, gp="Outcomes",
           fo=order_comp_out_fac, no=order_comp_out_num, c="structured only",
           agg=FALSE, ns=nsites)
```

#### Present in Chart Review Data Only
##### Prior Medical History
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_as_rest, num_comp_sfcr_as_rest, gp="Prior Medical History",
           fo=order_comp_med_fac, no=order_comp_med_num, c="chart only",
           agg=FALSE, ns=nsites)
```

##### Primary Procedure Characteristics
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_as_rest, num_comp_sfcr_as_rest, gp="Primary Procedure Characteristics",
           fo=order_comp_pro_fac, no=order_comp_pro_num, c="chart only",
           agg=FALSE, ns=nsites)
```

##### Outcomes
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_as_rest, num_comp_sfcr_as_rest, gp="Outcomes",
           fo=order_comp_out_fac, no=order_comp_out_num, c="chart only",
           agg=FALSE, ns=nsites)
```

#### Null in Both Structured and Chart Review Data
##### Prior Medical History
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_as_rest, num_comp_sfcr_as_rest, gp="Prior Medical History",
           fo=order_comp_med_fac, no=order_comp_med_num, c="both null",
           agg=FALSE, ns=nsites)
```

##### Primary Procedure Characteristics
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_as_rest, num_comp_sfcr_as_rest, gp="Primary Procedure Characteristics",
           fo=order_comp_pro_fac, no=order_comp_pro_num, c="both null",
           agg=FALSE, ns=nsites)
```

##### Outcomes
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_as_rest, num_comp_sfcr_as_rest, gp="Outcomes",
           fo=order_comp_out_fac, no=order_comp_out_num, c="both null",
           agg=FALSE, ns=nsites)
```

### NLP Approach: Retro-Pubic (RPMUS)
#### Present in Both Structured and Chart Review Data
##### Prior Medical History
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_ret_rest, num_comp_sfcr_ret_rest, gp="Prior Medical History",
           fo=order_comp_med_fac, no=order_comp_med_num, c="both present",
           agg=FALSE, ns=nsites)
```

##### Primary Procedure Characteristics
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_ret_rest, num_comp_sfcr_ret_rest, gp="Primary Procedure Characteristics",
           fo=order_comp_pro_fac, no=order_comp_pro_num, c="both present",
           agg=FALSE, ns=nsites)
```

##### Outcomes
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_ret_rest, num_comp_sfcr_ret_rest, gp="Outcomes",
           fo=order_comp_out_fac, no=order_comp_out_num, c="both present",
           agg=FALSE, ns=nsites)
```

#### Present in Structured Data Only
##### Prior Medical History
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_ret_rest, num_comp_sfcr_ret_rest, gp="Prior Medical History",
           fo=order_comp_med_fac, no=order_comp_med_num, c="structured only",
           agg=FALSE, ns=nsites)
```

##### Primary Procedure Characteristics
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_ret_rest, num_comp_sfcr_ret_rest, gp="Primary Procedure Characteristics",
           fo=order_comp_pro_fac, no=order_comp_pro_num, c="structured only",
           agg=FALSE, ns=nsites)
```

##### Outcomes
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_ret_rest, num_comp_sfcr_ret_rest, gp="Outcomes",
           fo=order_comp_out_fac, no=order_comp_out_num, c="structured only",
           agg=FALSE, ns=nsites)
```

#### Present in Chart Review Data Only
##### Prior Medical History
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_ret_rest, num_comp_sfcr_ret_rest, gp="Prior Medical History",
           fo=order_comp_med_fac, no=order_comp_med_num, c="chart only",
           agg=FALSE, ns=nsites)
```

##### Primary Procedure Characteristics
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_ret_rest, num_comp_sfcr_ret_rest, gp="Primary Procedure Characteristics",
           fo=order_comp_pro_fac, no=order_comp_pro_num, c="chart only",
           agg=FALSE, ns=nsites)
```

##### Outcomes
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_ret_rest, num_comp_sfcr_ret_rest, gp="Outcomes",
           fo=order_comp_out_fac, no=order_comp_out_num, c="chart only",
           agg=FALSE, ns=nsites)
```

#### Null in Both Structured and Chart Review Data
##### Prior Medical History
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_ret_rest, num_comp_sfcr_ret_rest, gp="Prior Medical History",
           fo=order_comp_med_fac, no=order_comp_med_num, c="both null",
           agg=FALSE, ns=nsites)
```

##### Primary Procedure Characteristics
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_ret_rest, num_comp_sfcr_ret_rest, gp="Primary Procedure Characteristics",
           fo=order_comp_pro_fac, no=order_comp_pro_num, c="both null",
           agg=FALSE, ns=nsites)
```

##### Outcomes
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_ret_rest, num_comp_sfcr_ret_rest, gp="Outcomes",
           fo=order_comp_out_fac, no=order_comp_out_num, c="both null",
           agg=FALSE, ns=nsites)
```

### NLP Approach: Single Incision (SIMUS)
#### Present in Both Structured and Chart Review Data
##### Prior Medical History
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_si_rest, num_comp_sfcr_si_rest, gp="Prior Medical History",
           fo=order_comp_med_fac, no=order_comp_med_num, c="both present",
           agg=FALSE, ns=nsites)
```

##### Primary Procedure Characteristics
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_si_rest, num_comp_sfcr_si_rest, gp="Primary Procedure Characteristics",
           fo=order_comp_pro_fac, no=order_comp_pro_num, c="both present",
           agg=FALSE, ns=nsites)
```

##### Outcomes
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_si_rest, num_comp_sfcr_si_rest, gp="Outcomes",
           fo=order_comp_out_fac, no=order_comp_out_num, c="both present",
           agg=FALSE, ns=nsites)
```

#### Present in Structured Data Only
##### Prior Medical History
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_si_rest, num_comp_sfcr_si_rest, gp="Prior Medical History",
           fo=order_comp_med_fac, no=order_comp_med_num, c="structured only",
           agg=FALSE, ns=nsites)
```

##### Primary Procedure Characteristics
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_si_rest, num_comp_sfcr_si_rest, gp="Primary Procedure Characteristics",
           fo=order_comp_pro_fac, no=order_comp_pro_num, c="structured only",
           agg=FALSE, ns=nsites)
```

##### Outcomes
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_si_rest, num_comp_sfcr_si_rest, gp="Outcomes",
           fo=order_comp_out_fac, no=order_comp_out_num, c="structured only",
           agg=FALSE, ns=nsites)
```

#### Present in Chart Review Data Only
##### Prior Medical History
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_si_rest, num_comp_sfcr_si_rest, gp="Prior Medical History",
           fo=order_comp_med_fac, no=order_comp_med_num, c="chart only",
           agg=FALSE, ns=nsites)
```

##### Primary Procedure Characteristics
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_si_rest, num_comp_sfcr_si_rest, gp="Primary Procedure Characteristics",
           fo=order_comp_pro_fac, no=order_comp_pro_num, c="chart only",
           agg=FALSE, ns=nsites)
```

##### Outcomes
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_si_rest, num_comp_sfcr_si_rest, gp="Outcomes",
           fo=order_comp_out_fac, no=order_comp_out_num, c="chart only",
           agg=FALSE, ns=nsites)
```

#### Null in Both Structured and Chart Review Data
##### Prior Medical History
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_si_rest, num_comp_sfcr_si_rest, gp="Prior Medical History",
           fo=order_comp_med_fac, no=order_comp_med_num, c="both null",
           agg=FALSE, ns=nsites)
```

##### Primary Procedure Characteristics
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_si_rest, num_comp_sfcr_si_rest, gp="Primary Procedure Characteristics",
           fo=order_comp_pro_fac, no=order_comp_pro_num, c="both null",
           agg=FALSE, ns=nsites)
```

##### Outcomes
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_si_rest, num_comp_sfcr_si_rest, gp="Outcomes",
           fo=order_comp_out_fac, no=order_comp_out_num, c="both null",
           agg=FALSE, ns=nsites)
```

### NLP Approach: Trans-Obturator (TOMUS)
#### Present in Both Structured and Chart Review Data
##### Prior Medical History
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_tra_rest, num_comp_sfcr_tra_rest, gp="Prior Medical History",
           fo=order_comp_med_fac, no=order_comp_med_num, c="both present",
           agg=FALSE, ns=nsites)
```

##### Primary Procedure Characteristics
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_tra_rest, num_comp_sfcr_tra_rest, gp="Primary Procedure Characteristics",
           fo=order_comp_pro_fac, no=order_comp_pro_num, c="both present",
           agg=FALSE, ns=nsites)
```

##### Outcomes
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_tra_rest, num_comp_sfcr_tra_rest, gp="Outcomes",
           fo=order_comp_out_fac, no=order_comp_out_num, c="both present",
           agg=FALSE, ns=nsites)
```

#### Present in Structured Data Only
##### Prior Medical History
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_tra_rest, num_comp_sfcr_tra_rest, gp="Prior Medical History",
           fo=order_comp_med_fac, no=order_comp_med_num, c="structured only",
           agg=FALSE, ns=nsites)
```

##### Primary Procedure Characteristics
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_tra_rest, num_comp_sfcr_tra_rest, gp="Primary Procedure Characteristics",
           fo=order_comp_pro_fac, no=order_comp_pro_num, c="structured only",
           agg=FALSE, ns=nsites)
```

##### Outcomes
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_tra_rest, num_comp_sfcr_tra_rest, gp="Outcomes",
           fo=order_comp_out_fac, no=order_comp_out_num, c="structured only",
           agg=FALSE, ns=nsites)
```

#### Present in Chart Review Data Only
##### Prior Medical History
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_tra_rest, num_comp_sfcr_tra_rest, gp="Prior Medical History",
           fo=order_comp_med_fac, no=order_comp_med_num, c="chart only",
           agg=FALSE, ns=nsites)
```

##### Primary Procedure Characteristics
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_tra_rest, num_comp_sfcr_tra_rest, gp="Primary Procedure Characteristics",
           fo=order_comp_pro_fac, no=order_comp_pro_num, c="chart only",
           agg=FALSE, ns=nsites)
```

##### Outcomes
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_tra_rest, num_comp_sfcr_tra_rest, gp="Outcomes",
           fo=order_comp_out_fac, no=order_comp_out_num, c="chart only",
           agg=FALSE, ns=nsites)
```

#### Null in Both Structured and Chart Review Data
##### Prior Medical History
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_tra_rest, num_comp_sfcr_tra_rest, gp="Prior Medical History",
           fo=order_comp_med_fac, no=order_comp_med_num, c="both null",
           agg=FALSE, ns=nsites)
```

##### Primary Procedure Characteristics
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_tra_rest, num_comp_sfcr_tra_rest, gp="Primary Procedure Characteristics",
           fo=order_comp_pro_fac, no=order_comp_pro_num, c="both null",
           agg=FALSE, ns=nsites)
```

##### Outcomes
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_tra_rest, num_comp_sfcr_tra_rest, gp="Outcomes",
           fo=order_comp_out_fac, no=order_comp_out_num, c="both null",
           agg=FALSE, ns=nsites)
```

### NLP Approach: Unknown
#### Present in Both Structured and Chart Review Data
##### Prior Medical History
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_un_rest, num_comp_sfcr_un_rest, gp="Prior Medical History",
           fo=order_comp_med_fac, no=order_comp_med_num, c="both present",
           agg=FALSE, ns=nsites)
```

##### Primary Procedure Characteristics
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_un_rest, num_comp_sfcr_un_rest, gp="Primary Procedure Characteristics",
           fo=order_comp_pro_fac, no=order_comp_pro_num, c="both present",
           agg=FALSE, ns=nsites)
```

##### Outcomes
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_un_rest, num_comp_sfcr_un_rest, gp="Outcomes",
           fo=order_comp_out_fac, no=order_comp_out_num, c="both present",
           agg=FALSE, ns=nsites)
```

#### Present in Structured Data Only
##### Prior Medical History
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_un_rest, num_comp_sfcr_un_rest, gp="Prior Medical History",
           fo=order_comp_med_fac, no=order_comp_med_num, c="structured only",
           agg=FALSE, ns=nsites)
```

##### Primary Procedure Characteristics
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_un_rest, num_comp_sfcr_un_rest, gp="Primary Procedure Characteristics",
           fo=order_comp_pro_fac, no=order_comp_pro_num, c="structured only",
           agg=FALSE, ns=nsites)
```

##### Outcomes
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_un_rest, num_comp_sfcr_un_rest, gp="Outcomes",
           fo=order_comp_out_fac, no=order_comp_out_num, c="structured only",
           agg=FALSE, ns=nsites)
```

#### Present in Chart Review Data Only
##### Prior Medical History
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_un_rest, num_comp_sfcr_un_rest, gp="Prior Medical History",
           fo=order_comp_med_fac, no=order_comp_med_num, c="chart only",
           agg=FALSE, ns=nsites)
```

##### Primary Procedure Characteristics
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_un_rest, num_comp_sfcr_un_rest, gp="Primary Procedure Characteristics",
           fo=order_comp_pro_fac, no=order_comp_pro_num, c="chart only",
           agg=FALSE, ns=nsites)
```

##### Outcomes
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_un_rest, num_comp_sfcr_un_rest, gp="Outcomes",
           fo=order_comp_out_fac, no=order_comp_out_num, c="chart only",
           agg=FALSE, ns=nsites)
```

#### Null in Both Structured and Chart Review Data
##### Prior Medical History
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_un_rest, num_comp_sfcr_un_rest, gp="Prior Medical History",
           fo=order_comp_med_fac, no=order_comp_med_num, c="both null",
           agg=FALSE, ns=nsites)
```

##### Primary Procedure Characteristics
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_un_rest, num_comp_sfcr_un_rest, gp="Primary Procedure Characteristics",
           fo=order_comp_pro_fac, no=order_comp_pro_num, c="both null",
           agg=FALSE, ns=nsites)
```

##### Outcomes
Columns summarize n (%)
```{r, results='asis'}
print_comp(factor_comp_sfcr_un_rest, num_comp_sfcr_un_rest, gp="Outcomes",
           fo=order_comp_out_fac, no=order_comp_out_num, c="both null",
           agg=FALSE, ns=nsites)
```

## Concordance by Site
### Overall
#### Prior Medical History
Columns summarize n (%) concordant or mean difference (SD) where applicable. 
```{r}
print_concord(dat_factor=factor_comp_sfcr_rest, dat_numeric=num_comp_sfcr_rest,
              gp="Prior Medical History", fo=order_comp_med_fac,
              no=order_comp_med_num)
```

#### Primary Procedure Characteristics
Columns summarize n (%) concordant or mean difference (SD) where applicable. 
```{r}
print_concord(dat_factor=factor_comp_sfcr_rest, dat_numeric=num_comp_sfcr_rest,
              gp="Primary Procedure Characteristics", fo=order_comp_pro_fac,
              no=order_comp_pro_num)
```

#### Outcomes
Columns summarize n (%) concordant or mean difference (SD) where applicable. 
```{r}
print_concord(dat_factor=factor_comp_sfcr_rest, dat_numeric=num_comp_sfcr_rest,
              gp="Outcomes", fo=order_comp_out_fac,
              no=order_comp_out_num)
```

### NLP Approach: Adjustable Sling (AMUS)
#### Prior Medical History
Columns summarize n (%) concordant or mean difference (SD) where applicable. 
```{r}
print_concord(dat_factor=factor_comp_sfcr_as_rest, dat_numeric=num_comp_sfcr_as_rest,
              gp="Prior Medical History", fo=order_comp_med_fac,
              no=order_comp_med_num)
```

#### Primary Procedure Characteristics
Columns summarize n (%) concordant or mean difference (SD) where applicable. 
```{r}
print_concord(dat_factor=factor_comp_sfcr_as_rest, dat_numeric=num_comp_sfcr_as_rest,
              gp="Primary Procedure Characteristics", fo=order_comp_pro_fac,
              no=order_comp_pro_num)
```

#### Outcomes
Columns summarize n (%) concordant or mean difference (SD) where applicable. 
```{r}
print_concord(dat_factor=factor_comp_sfcr_as_rest, dat_numeric=num_comp_sfcr_as_rest,
              gp="Outcomes", fo=order_comp_out_fac,
              no=order_comp_out_num)
```

### NLP Approach: Retro-Pubic (RPMUS)
#### Prior Medical History
Columns summarize n (%) concordant or mean difference (SD) where applicable. 
```{r}
print_concord(dat_factor=factor_comp_sfcr_ret_rest, dat_numeric=num_comp_sfcr_ret_rest,
              gp="Prior Medical History", fo=order_comp_med_fac,
              no=order_comp_med_num)
```

#### Primary Procedure Characteristics
Columns summarize n (%) concordant or mean difference (SD) where applicable. 
```{r}
print_concord(dat_factor=factor_comp_sfcr_ret_rest, dat_numeric=num_comp_sfcr_ret_rest,
              gp="Primary Procedure Characteristics", fo=order_comp_pro_fac,
              no=order_comp_pro_num)
```

#### Outcomes
Columns summarize n (%) concordant or mean difference (SD) where applicable. 
```{r}
print_concord(dat_factor=factor_comp_sfcr_ret_rest, dat_numeric=num_comp_sfcr_ret_rest,
              gp="Outcomes", fo=order_comp_out_fac,
              no=order_comp_out_num)
```

### NLP Approach: Single Incision (SIMUS)
#### Prior Medical History
Columns summarize n (%) concordant or mean difference (SD) where applicable. 
```{r}
print_concord(dat_factor=factor_comp_sfcr_si_rest, dat_numeric=num_comp_sfcr_si_rest,
              gp="Prior Medical History", fo=order_comp_med_fac,
              no=order_comp_med_num)
```

#### Primary Procedure Characteristics
Columns summarize n (%) concordant or mean difference (SD) where applicable. 
```{r}
print_concord(dat_factor=factor_comp_sfcr_si_rest, dat_numeric=num_comp_sfcr_si_rest,
              gp="Primary Procedure Characteristics", fo=order_comp_pro_fac,
              no=order_comp_pro_num)
```

#### Outcomes
Columns summarize n (%) concordant or mean difference (SD) where applicable. 
```{r}
print_concord(dat_factor=factor_comp_sfcr_si_rest, dat_numeric=num_comp_sfcr_si_rest,
              gp="Outcomes", fo=order_comp_out_fac,
              no=order_comp_out_num)
```

### NLP Approach: Trans-Obturator (TOMUS)
#### Prior Medical History
Columns summarize n (%) concordant or mean difference (SD) where applicable. 
```{r}
print_concord(dat_factor=factor_comp_sfcr_tra_rest, dat_numeric=num_comp_sfcr_tra_rest,
              gp="Prior Medical History", fo=order_comp_med_fac,
              no=order_comp_med_num)
```

#### Primary Procedure Characteristics
Columns summarize n (%) concordant or mean difference (SD) where applicable. 
```{r}
print_concord(dat_factor=factor_comp_sfcr_tra_rest, dat_numeric=num_comp_sfcr_tra_rest,
              gp="Primary Procedure Characteristics", fo=order_comp_pro_fac,
              no=order_comp_pro_num)
```

#### Outcomes
Columns summarize n (%) concordant or mean difference (SD) where applicable. 
```{r}
print_concord(dat_factor=factor_comp_sfcr_tra_rest, dat_numeric=num_comp_sfcr_tra_rest,
              gp="Outcomes", fo=order_comp_out_fac,
              no=order_comp_out_num)
```

### NLP Approach: Unknown
#### Prior Medical History
Columns summarize n (%) concordant or mean difference (SD) where applicable. 
```{r}
print_concord(dat_factor=factor_comp_sfcr_un_rest, dat_numeric=num_comp_sfcr_un_rest,
              gp="Prior Medical History", fo=order_comp_med_fac,
              no=order_comp_med_num)
```

#### Primary Procedure Characteristics
Columns summarize n (%) concordant or mean difference (SD) where applicable. 
```{r}
print_concord(dat_factor=factor_comp_sfcr_un_rest, dat_numeric=num_comp_sfcr_un_rest,
              gp="Primary Procedure Characteristics", fo=order_comp_pro_fac,
              no=order_comp_pro_num)
```

#### Outcomes
Columns summarize n (%) concordant or mean difference (SD) where applicable. 
```{r}
print_concord(dat_factor=factor_comp_sfcr_un_rest, dat_numeric=num_comp_sfcr_un_rest,
              gp="Outcomes", fo=order_comp_out_fac,
              no=order_comp_out_num)
```

## Aggregate Data Availability
### Overall
#### Prior Medical History
Columns summarize n (row %) present. 
```{r, results='asis'}
print_comp(factor_comp_sfcr_rest, num_comp_sfcr_rest, gp="Prior Medical History", 
           fo=order_comp_med_fac, no=order_comp_med_num, c="na", agg=TRUE, ns=nsites_c)
```

#### Primary Procedure Characteristics
Columns summarize n (row %) present. 
```{r, results='asis'}
print_comp(factor_comp_sfcr_rest, num_comp_sfcr_rest, gp="Primary Procedure Characteristics", 
           fo=order_comp_pro_fac, no=order_comp_pro_num, c="na", agg=TRUE, ns=nsites_c)
```

#### Outcomes
Columns summarize n (row %) present. 
```{r, results='asis'}
print_comp(factor_comp_sfcr_rest, num_comp_sfcr_rest, gp="Outcomes", 
           fo=order_comp_out_fac, no=order_comp_out_num, c="na", agg=TRUE, ns=nsites_c)
```

### NLP Approach: Adjustable Sling (AMUS)
#### Prior Medical History
Columns summarize n (row %) present.
```{r, results='asis'}
print_comp(factor_comp_sfcr_as_rest, num_comp_sfcr_as_rest, gp="Prior Medical History", 
           fo=order_comp_med_fac, no=order_comp_med_num, c="na", agg=TRUE, ns=nsites)
```

#### Primary Procedure Characteristics
Columns summarize n (row %) present.
```{r, results='asis'}
print_comp(factor_comp_sfcr_as_rest, num_comp_sfcr_as_rest, gp="Primary Procedure Characteristics", 
           fo=order_comp_pro_fac, no=order_comp_pro_num, c="na", agg=TRUE, ns=nsites)
```

#### Outcomes
Columns summarize n (row %) present.
```{r, results='asis'}
print_comp(factor_comp_sfcr_as_rest, num_comp_sfcr_as_rest, gp="Outcomes", 
           fo=order_comp_out_fac, no=order_comp_out_num, c="na", agg=TRUE, ns=nsites)
```

### NLP Approach: Retro-Pubic (RPMUS)
#### Prior Medical History
Columns summarize n (row %) present.
```{r, results='asis'}
print_comp(factor_comp_sfcr_ret_rest, num_comp_sfcr_ret_rest, gp="Prior Medical History", 
           fo=order_comp_med_fac, no=order_comp_med_num, c="na", agg=TRUE, ns=nsites)
```

#### Primary Procedure Characteristics
Columns summarize n (row %) present.
```{r, results='asis'}
print_comp(factor_comp_sfcr_ret_rest, num_comp_sfcr_ret_rest, gp="Primary Procedure Characteristics", 
           fo=order_comp_pro_fac, no=order_comp_pro_num, c="na", agg=TRUE, ns=nsites)
```

#### Outcomes
Columns summarize n (row %) present.
```{r, results='asis'}
print_comp(factor_comp_sfcr_ret_rest, num_comp_sfcr_ret_rest, gp="Outcomes", 
           fo=order_comp_out_fac, no=order_comp_out_num, c="na", agg=TRUE, ns=nsites)
```

### NLP Approach: Single Incision (SIMUS)
#### Prior Medical History
Columns summarize n (row %) present.
```{r, results='asis'}
print_comp(factor_comp_sfcr_si_rest, num_comp_sfcr_si_rest, gp="Prior Medical History", 
           fo=order_comp_med_fac, no=order_comp_med_num, c="na", agg=TRUE, ns=nsites)
```

#### Primary Procedure Characteristics
Columns summarize n (row %) present.
```{r, results='asis'}
print_comp(factor_comp_sfcr_si_rest, num_comp_sfcr_si_rest, gp="Primary Procedure Characteristics", 
           fo=order_comp_pro_fac, no=order_comp_pro_num, c="na", agg=TRUE, ns=nsites)
```

#### Outcomes
Columns summarize n (row %) present.
```{r, results='asis'}
print_comp(factor_comp_sfcr_si_rest, num_comp_sfcr_si_rest, gp="Outcomes", 
           fo=order_comp_out_fac, no=order_comp_out_num, c="na", agg=TRUE, ns=nsites)
```

### NLP Approach: Trans-Obturator (TOMUS)
#### Prior Medical History
Columns summarize n (row %) present.
```{r, results='asis'}
print_comp(factor_comp_sfcr_tra_rest, num_comp_sfcr_tra_rest, gp="Prior Medical History", 
           fo=order_comp_med_fac, no=order_comp_med_num, c="na", agg=TRUE, ns=nsites)
```

#### Primary Procedure Characteristics
Columns summarize n (row %) present.
```{r, results='asis'}
print_comp(factor_comp_sfcr_tra_rest, num_comp_sfcr_tra_rest, gp="Primary Procedure Characteristics", 
           fo=order_comp_pro_fac, no=order_comp_pro_num, c="na", agg=TRUE, ns=nsites)
```

#### Outcomes
Columns summarize n (row %) present.
```{r, results='asis'}
print_comp(factor_comp_sfcr_tra_rest, num_comp_sfcr_tra_rest, gp="Outcomes", 
           fo=order_comp_out_fac, no=order_comp_out_num, c="na", agg=TRUE, ns=nsites)
```

### NLP Approach: Unknown
#### Prior Medical History
Columns summarize n (row %) present.
```{r, results='asis'}
print_comp(factor_comp_sfcr_un_rest, num_comp_sfcr_un_rest, gp="Prior Medical History", 
           fo=order_comp_med_fac, no=order_comp_med_num, c="na", agg=TRUE, ns=nsites)
```

#### Primary Procedure Characteristics
Columns summarize n (row %) present.
```{r, results='asis'}
print_comp(factor_comp_sfcr_un_rest, num_comp_sfcr_un_rest, gp="Primary Procedure Characteristics", 
           fo=order_comp_pro_fac, no=order_comp_pro_num, c="na", agg=TRUE, ns=nsites)
```

#### Outcomes
Columns summarize n (row %) present.
```{r, results='asis'}
print_comp(factor_comp_sfcr_un_rest, num_comp_sfcr_un_rest, gp="Outcomes", 
           fo=order_comp_out_fac, no=order_comp_out_num, c="na", agg=TRUE, ns=nsites)
```

## Aggregate Concordance
### Prior Medical History
Columns summarize percent concordant (95% CI) or mean difference (SD) where applicable. 
```{r}
print_concord(fmr=factor_comp_sfcr_rest, far=factor_comp_sfcr_as_rest,
              frr=factor_comp_sfcr_ret_rest, fir=factor_comp_sfcr_si_rest,
              ftr=factor_comp_sfcr_tra_rest, fur=factor_comp_sfcr_un_rest,
              nmr=num_comp_sfcr_rest, nar=num_comp_sfcr_as_rest,
              nrr=num_comp_sfcr_ret_rest, nir=num_comp_sfcr_si_rest,
              ntr=num_comp_sfcr_tra_rest, nur=num_comp_sfcr_un_rest,
              gp="Prior Medical History", fo=order_comp_med_fac, 
              no=order_comp_med_num, agg=TRUE, ns=nsites, nsc=nsites_c)
```

### Primary Procedure Characteristics
Columns summarize percent concordant (95% CI) or mean difference (SD) where applicable.
```{r}
print_concord(fmr=factor_comp_sfcr_rest, far=factor_comp_sfcr_as_rest,
              frr=factor_comp_sfcr_ret_rest, fir=factor_comp_sfcr_si_rest,
              ftr=factor_comp_sfcr_tra_rest, fur=factor_comp_sfcr_un_rest,
              nmr=num_comp_sfcr_rest, nar=num_comp_sfcr_as_rest,
              nrr=num_comp_sfcr_ret_rest, nir=num_comp_sfcr_si_rest,
              ntr=num_comp_sfcr_tra_rest, nur=num_comp_sfcr_un_rest,
              gp="Primary Procedure Characteristics", fo=order_comp_pro_fac, 
              no=order_comp_pro_num, agg=TRUE, ns=nsites, nsc=nsites_c)
```    

### Outcomes
Columns summarize percent concordant (95% CI) or mean difference (SD) where applicable. 
```{r hbjd4}
print_concord(fmr=factor_comp_sfcr_rest, far=factor_comp_sfcr_as_rest,
              frr=factor_comp_sfcr_ret_rest, fir=factor_comp_sfcr_si_rest,
              ftr=factor_comp_sfcr_tra_rest, fur=factor_comp_sfcr_un_rest,
              nmr=num_comp_sfcr_rest, nar=num_comp_sfcr_as_rest,
              nrr=num_comp_sfcr_ret_rest, nir=num_comp_sfcr_si_rest,
              ntr=num_comp_sfcr_tra_rest, nur=num_comp_sfcr_un_rest,
              gp="Outcomes", fo=order_comp_out_fac, 
              no=order_comp_out_num, agg=TRUE, ns=nsites, nsc=nsites_c)
```

# Chart Review Validation of NLP Approach & Mesh
## Approach
Columns summarize % concordant (% true positive, % true negative, % false positive, % false negative).
```{r, results='asis'}
print_valid(factor_comp_rscr, fo=order_comp_app_rscr, ns=nsites) 
```

## Mesh
Columns summarize % concordant (% true positive, % true negative, % false positive, % false negative).
```{r, results='asis'}
print_valid(factor_comp_rscr, fo=order_comp_pro_rscr, ns=nsites) 
```

# Chart Review Validation of EHR Mesh
Columns summarize % concordant (% true positive, % true negative, % false positive, % false negative).
```{r, results='asis'}
print_valid(factor_comp_sscr, fo=order_comp_pro_fac, ns=nsites) 
```

# Computing Environment
`r mu$session()`